### 2009-11-27 doc/tech_doc/a-rex/arex_tech_doc.tex
add note to wakeupperiod option
fix example config in a-rex manual

in seconds. Default is \emph{3 minutes}.

@@

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/ArcConfig/2007"
  xmlns:tcp="http://www.nordugrid.org/schemas/ArcMCCTCP/2007"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/Config"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>VERBOSE</Level>
      <File>/var/log/arched.log</File>
      <Backups>10</Backups>
      <Maxsize>100000000</Maxsize>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <ModuleManager>
    <Path>/usr/local/lib/arc/</Path>
  </ModuleManager>
  <!-- Simply load all needed plugins -->
  <Plugins><Name>mcctcp</Name></Plugins>
  <Plugins><Name>mcctls</Name></Plugins>
  <Plugins><Name>mcchttp</Name></Plugins>
  <Plugins><Name>mccsoap</Name></Plugins>
  <Plugins><Name>arcpdc</Name></Plugins>
  <Plugins><Name>identitymap</Name></Plugins>
  <Plugins><Name>arex</Name></Plugins>
  <!-- Create a chain -->
  <Chain>
    <!-- TCP listening socket -->
    <Component name="tcp.service" id="tcp">
      <next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </Component>
    <!-- Transport-level security -->
    <Component name="tls.service" id="tls">
      <next id="http"/>
      <!-- Location of server's security keys -->
      <KeyPath>/etc/grid-security/hostkey.pem</KeyPath>
      <CertificatePath>/etc/grid-security/hostcert.pem</CertificatePath>
      <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
           Comment it if no user mapping is needed. -->
      <SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <PDP name="allow.pdp"><LocalName>nobody</LocalName></PDP>
      </SecHandler>
    </Component>
    <!-- HTTP processing is done here -->
    <Component name="http.service" id="http">
      <next id="soap">POST</next>
      <next id="plexer">GET</next>
      <next id="plexer">PUT</next>
    </Component>
    <!-- This one parses content into XML tree -->
    <Component name="soap.service" id="soap">
      <next id="plexer"/>
    </Component>
    <!-- Directing messages to proper service -->
    <Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
           Unmatched part of path is propagated to service in
           PLEXER:EXTENSION attribute. -->
      <next id="a-rex">^/arex</next>
    </Plexer>
    <!-- A-Rex service -->
    <Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
           Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </Service>
  </Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}

>>>>

in seconds. Default is \emph{3 minutes}. The A-REX may also be woken up by
external processes such as LRMS scripts before this time period expires.

@@

\begin{shaded}
\begin{verbatim}
<?xml version="1.0"?>
<ArcConfig
  xmlns="http://www.nordugrid.org/schemas/arcconfig/2009/08"
  xmlns:loader="http://www.nordugrid.org/schemas/loader/2009/08"
  xmlns:arex="http://www.nordugrid.org/schemas/a-rex/2009/08"
  xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
  xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
  xmlns:authz="http://www.nordugrid.org/schemas/arcauthz/2009/08"
  xmlns:idmap="http://www.nordugrid.org/schemas/identitymap/2009/10"
>
  <!-- Common configuration of the daemon -->
  <Server>
    <PidFile>/var/run/arched.pid</PidFile>
    <Logger>
      <Level>VERBOSE</Level>
      <File>/var/log/arched.log</File>
      <MaxSize>100000000</MaxSize>
      <Backups>10</Backups>
    </Logger>
  </Server>
  <!-- Where to find plugins -->
  <loader:ModuleManager>
    <loader:Path>/usr/local/lib/arc/</loader:Path>
  </loader:ModuleManager>
  <!-- Simply load all needed plugins -->
  <loader:Plugins>
    <loader:Name>mcctcp</loader:Name>
    <loader:Name>mcctls</loader:Name>
    <loader:Name>mcchttp</loader:Name>
    <loader:Name>mccsoap</loader:Name>
    <loader:Name>arcpdc</loader:Name>
    <loader:Name>identitymap</loader:Name>
    <loader:Name>arex</loader:Name>
  </loader:Plugins>
  <!-- Create a chain -->
  <loader:Chain>
    <!-- TCP listening socket -->
    <loader:Component name="tcp.service" id="tcp">
      <loader:next id="tls"/>
      <tcp:Listen><tcp:Port>60000</tcp:Port></tcp:Listen>
    </loader:Component>
    <!-- Transport-level security -->
    <loader:Component name="tls.service" id="tls">
      <loader:next id="http"/>
      <!-- Location of server's security keys -->
      <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
      <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
      <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
      <!-- Evaluate requestor's identity into local identity.
      Comment it if no user mapping is needed. -->
      <loader:SecHandler name="identity.map" id="map" event="incoming">
        <!-- Safe choice if all other rules failed -->
        <idmap:PDP name="allow.pdp"><idmap:LocalName>nobody</idmap:LocalName></idmap:PDP>
      </loader:SecHandler>
    </loader:Component>
    <!-- HTTP processing is done here -->
    <loader:Component name="http.service" id="http">
      <loader:next id="soap">POST</loader:next>
      <loader:next id="plexer">GET</loader:next>
      <loader:next id="plexer">PUT</loader:next>
    </loader:Component>
    <!-- This one parses content into XML tree -->
    <loader:Component name="soap.service" id="soap">
      <loader:next id="plexer"/>
    </loader:Component>
    <!-- Directing messages to proper service -->
    <loader:Plexer name="plexer.service" id="plexer">
      <!-- RegExp pattern is matched to path part of endpoint.
      Unmatched part of path is propagated to service in
      PLEXER:EXTENSION attribute. -->
      <loader:next id="a-rex">^/arex</loader:next>
    </loader:Plexer>
    <!-- A-Rex service -->
    <loader:Service name="a-rex" id="a-rex">
      <!-- Optional endpoint element is advised in case of multiple IP adresses -->
      <arex:endpoint>https://localhost:60000/arex</arex:endpoint>
      <!-- Use information generated by identity.map plugin or default provided below -->
      <arex:usermap><arex:defaultLocalName>nobody</arex:defaultLocalName></arex:usermap>
      <!-- grid-manager part of a-rex requires legacy configuration file.
      Use arc.conf example or write own. -->
      <arex:gmconfig>/etc/arc.conf</arex:gmconfig>
    </loader:Service>
  </loader:Chain>
</ArcConfig>
\end{verbatim}
\end{shaded}
